### 2013-04-07 writing/article.Rmd
final draft :)

```{r fig.width=10, fig.height=4, echo=FALSE}
library(png)
library(grid)
img <- readPNG("../writing/figure/density.png")
grid.raster(img)
```
**Рисунок 3.** Плотность распределения оценок по выбранным странам

>>>>

```{r fig.width=10, fig.height=4, echo=FALSE}
library(png)
library(grid)
img <- readPNG("../writing/figure/density.low.png")
grid.raster(img)
```
```{r fig.width=10, fig.height=4, echo=FALSE}
library(png)
library(grid)
img <- readPNG("../writing/figure/density.high.png")
grid.raster(img)
```
**Рисунок 3.** Плотность распределения оценок по выбранным странам
